\begin{thebibliography}{99}
\bibitem{Baaj-Julg} Baaj, S., Julg, P. {\it Th\'eorie bivariante de Kasparov et op\'erateurs non born\'es dans les $C^*$-modules hilbertiens.} C. R. Acad. Sci. Paris S\'er. I Math. {\bf 296} (1983), no. 21, 875--878.
\bibitem{BF} Benameur M., Fack T. {\it Type II non-commutative geometry. I. Dixmier trace in von Neumann algebras.} Adv. Math. {\bf 199} (2006), no. 1, 29--87.
\bibitem{Bennet-Sharpley-interpolation-1988} Bennett C., Sharpley R. {\it Interpolation of operators.} volume 129 of {\it Pure and Applied Mathematics}, Academic Press, Inc., Boston, MA, 1988.
\bibitem{Birman-Solomyak-I} Birman M., Solomyak M. {\it Double Stieltjes operator integrals.} In {\it Problems of Mathematical Physics, No. I, Spectral Theory and Wave Processes} (Russian), pp. 33--67. Izdat. Leningrad. Univ., Leningrad, 1966.
\bibitem{Birman-Solomyak-II} Birman M., Solomyak M. {\it Double Stieltjes operator integrals. II} In {\em Problems of Mathematical Physics, No. 2, Spectral Theory, Diffraction Problems}  (Russian), pp. 26--60. Izdat. Leningrad. Univ., Leningrad, 1967.
\bibitem{Birman-Solomyak-III}  Birman M., Solomyak M. {\it Double Stieltjes operator integrals. III.} In {\it Problems of mathematical physics, No. 6} (Russian), pp. 27--53. Izdat. Leningrad. Univ., Leningrad, 1973. 
\bibitem{Birman-Solomyak-2003} Birman M., Solomyak M. {\it Double operator integrals in a Hilbert space.} Int. Eq. Oper. Th.  {\bf 47} (2) 131--168, 2003.
\bibitem{Bratteli-Robinson1} Bratteli O., Robinson D. {\it Operator algebras and quantum statistical mechanics. 1. $C^*-$ and $W^*-$algebras, symmetry groups, decomposition of states.} Texts and Monographs in Physics. Springer-Verlag, 1987.
\bibitem{Bratteli-Robinson2} Bratteli O., Robinson D. {\it Operator algebras and quantum statistical mechanics. 2}. Texts and Monographs in Physics. Springer-Verlag, 1997.
\newblock Equilibrium states. Models in quantum statistical mechanics.
\bibitem{CGRS1} Carey A., Gayral V., Rennie A., Sukochev F. {\it Integration on locally compact noncommutative spaces.} J. Funct. Anal. {\bf 263} (2012), no. 2, 383--414.
\bibitem{CGRS2} Carey A., Gayral V., Rennie A., Sukochev F. {\it Index theory for locally compact noncommutative geometries.} Mem. Amer. Math. Soc. {\bf 231} (2014), no. 1085, vi+130 pp.
\bibitem{CPRS1} Carey A., Phillips J., Rennie A., Sukochev F. {\it The Hochschild class of the Chern character for semifinite spectral triples.} J. Funct. Anal. {\bf 213} (2004), no. 1, 111--153.
\bibitem{CPRS2} Carey A., Phillips J., Rennie A., Sukochev F., {\it The local index formula in semifinite von Neumann algebras. I. Spectral flow.} Adv. Math. {\bf 202} (2006), no. 2, 451--516. 
\bibitem{CPRS4} Carey A., Phillips J., Rennie A., Sukochev F., {\it The Chern character of semifinite spectral triples.} J. Noncommut. Geom. {\bf 2} (2008), no. 2, 141--193.
\bibitem{CRSZ} Carey A., Rennie A., Sukochev F., Zanin D. {\it Universal measurability and the Hochschild class of the Chern character.} J. Spectr. Theory {\bf 6} (2016), no. 1, 1--41.
\bibitem{Connes-Chamseddine-Mukhanov-quanta-of-geometry-2015} Chamseddine, A., Connes, A., Mukhanov, V. {\it Quanta of geometry: noncommutative aspects.} Phys. Rev. Lett. {\bf 114} (2015), no. 9, 091302, 5pp.
\bibitem{Connes-differential-geometry} Connes, A. {\it Noncommutative differential geometry.} Inst. Hautes \'Etudes Sci. Publ. Math. {\bf 62} (1985), 247--360.
\bibitem{Connes-original-spectral-1995} Connes A. {\it Geometry from the spectral point of view.} Lett. Math. Phys., {\bf 34} (3) 203--238, 1995.
\bibitem{NCG-book} Connes A. {\it Noncommutative geometry.} Academic Press, Inc., San Diego, CA, 1994.
\bibitem{Connes-nuclear} Connes A., {\it Trace de Dixmier, modules de Fredholm et geometrie riemannienne.} Nuclear Phys. B Proc. Suppl. 5B (1988), 65--70.
\bibitem{Connes-course} Connes A., Cours au College de France, 1990.
\bibitem{Connes-reality} Connes A., {\it Noncommutative geometry and reality.} J. Math. Phys. {\bf 36} (1995), 6194–-6231 .
\bibitem{Connes-reconstruction} Connes A., {\it On the spectral characterization of manifolds.} J. Noncommut. Geom. {\bf 7} (2013), no. 1, 1--82.
\bibitem{Connes-Moscovici} Connes A., Moscovici H., {\it The local index formula in noncommutative geometry.} Geom. Funct. Anal. {\bf 5} (1995), no. 2, 174--243.
\bibitem{CSZ} Connes A., Sukochev F., Zanin D., {\it Trace theorem for quasi-Fuchsian groups.} Sb. Math. {\bf 208} (2017), no. 10, 1473--1502.
\bibitem{chernov}  Chernoff P. {\it Essential self-adjointness of powers of generators of hyperbolic equations.} J. Functional Analysis {\bf 12} (1973), 401--414.
\bibitem{cwikel} Cwikel M. {\it Weak type estimates for singular values and the number of bound states of Schr\"odinger operators.} Ann. of Math. (2) {\bf 106} (1977), no. 1, 93--100.
\bibitem{Dixmier} Dixmier J. {\it Existence de traces non normales.} (French)  C. R. Acad. Sci. Paris Ser. A-B  {\bf 262}  (1966) A1107--A1108.
\bibitem{Dunford-Schwartz-1} Dunford N., Schwartz J., {\it Linear Operators, Part I: General theory.} John Wiley and Sons, Inc., New York, 1988.
\bibitem{Frohlich-Grandjean-Recknagel} Fr\"ohlich J., Grandjean, O., Recknagel, A. {\it Supersymmetric quantum theory and non-commutative geometry.} Comm. Math. Phys. {\bf 203} (1999), no. 1, 119--184.
\bibitem{gayral-moyal} Gayral V., Gracia-Bondia J., Iochum B., Sch\"ucker T., Varilly J. {\it Moyal planes are spectral triples.} Comm. Math. Phys. {\bf 246} (2004), no. 3, 569--623.
\bibitem{GIV} Gayral V., Iochum B., Varilly J., {\it Dixmier traces on noncompact isospectral deformations.} J. Funct. Anal. {\bf 237} (2006), no. 2, 507--539.
\bibitem{GVF} Gracia-Bondia J., Varilly J., Figueroa H. {\it Elements of noncommutative geometry.} Birkhäuser Boston, Inc., Boston, MA, 2001.
\bibitem{higson}  Higson N. {\it The residue index theorem of Connes and Moscovici.} Surveys in noncommutative geometry, 71--126, Clay Math. Proc., {\bf 6}, Amer. Math. Soc., Providence, RI, 2006.
\bibitem{DFWW} Dykema K., Figiel T., Weiss G., Wodzicki M. {\it Commutator structure of operator ideals.}  Adv. Math. {\bf 185} (2004), no. 1, 1--79.
\bibitem{Echterhoff-2008} Echterhoff S. {\it The $K$-theory of twisted group algebras.} In {\it $C^\ast$-algebras and elliptic theory II}, Trends Math., pp 67--86. Birkh\"auser, Basel, 2008.
\bibitem{KLPS} Kalton N., Lord S., Potapov D., Sukochev F. {\it Traces of compact operators and the noncommutative residue.} Adv. Math. {\bf 235} (2013), 1--55.
\bibitem{krym} Kordyukov Y. {\it Differential operators on manifolds and their applications in geometry and topology.} Proceedings of Crimean Autumn School, 2009. 
\bibitem{Kosaki-alt-1992} Kosaki H. {\it An inequality of Araki-Lieb-Thirring (von Neumann algebra case).} Proc. Amer. Math. Soc., {\bf 114} (2) 477--481, 1992.
\bibitem{Landi} Landi G. {\it An introduction to noncommutative spaces and their geometries.} Lecture Notes in Physics. New Series m: Monographs, {\bf 51}. Springer-Verlag, Berlin, 1997.
\bibitem{Lawson-Michelsohn-1989} Lawson B., Michelsohn M., {\it Spin geometry.} Princeton Mathematical Series, {\bf 38}. Princeton University Press, Princeton, NJ, 1989.
\bibitem{LeSZ-cwikel} Levitina G., Sukochev F., Zanin D. {\it Cwikel estimates revisited.} submitted manuscript. arXiv:1703.04254
\bibitem{Loday-cyclic-homology} Loday J. {\it Cyclic homology.} volume 301 of Grundlehren der Mathematischen Wissenschaften, Springer-Verlag, 1998.
\bibitem{Lord-Rennie-Varilly} Lord S., Rennie A., V\'arilly J., {\it Riemannian manifolds in noncommutative geometry.} J. Geom. Phys, {\bf 62} (2012), no. 7, 1611--1638
\bibitem{LSZ} Lord S., Sukochev F., Zanin D. {\it Singular Traces: Theory and Applications.} volume 46 of Studies in Mathematics. De Gruyter, 2013.
\bibitem{PSW} de Pagter B., Sukochev F., Witvliet H. {\it Double operator integrals.} J. Funct.Anal. {\bf 192} (2002), no. 1, 52--111.
\bibitem{peller} Peller V. {\it Hankel operators in the theory of perturbations of unitary and selfadjoint operators.} Funktsional. Anal. i Prilozhen. {\bf 19} (1985), no. 2, 37--51, 96.
\bibitem{Peller-doi-2016} Peller V. {\it Multiple operator integrals in perturbation theory.} Bull. Math. Sci., {\bf 6} (1) 15--88, 2016.
\bibitem{Pflaum-continuous-hh-1998} Pflaum M. {\it On continuous Hochschild homology and cohomology groups.} Lett. Math. Phys., {\bf 44} (1) 43--51, 1998.
\bibitem{PS-acta} Potapov D., Sukochev F. {\it Operator-Lipschitz functions in Schatten-von Neumann classes.} Acta Math. {\bf 207} (2011), no. 2, 375--389.
\bibitem{PS-crelle} Potapov D., Sukochev F. {\it Unbounded Fredholm modules and double operator integrals.} J. Reine Angew. Math. {\bf 626} (2009), 159--185.
\bibitem{Quillen} Quillen D. {\it Algebra cochains and cyclic cohomology.} Inst. Hautes \'Etudes Sci. Publ. Math. {\bf 68} (1989), 139--174.        
\bibitem{Reed-Simon-I-1980} Reed M., Simon B. {\it Methods of modern mathematical physics. I.} Academic Press, New York, second edition, 1980.
\bibitem{Rennie-2003} Rennie, A. {\it Smoothness and locality for nonunital spectral triples.} K-Theory {\bf 28} (2003), no. 2, 127-–165. 
\bibitem{Rennie-2004} Rennie, A. {\it Summability for nonunital spectral triples. } K-Theory {\bf 31} (2004), no. 1, 71-–100.
\bibitem{rosenberg} Rosenberg S. {\it The Laplacian on a Riemannian manifold. An introduction to analysis on manifolds.} London Mathematical Society Student Texts, {\bf 31}. Cambridge University Press, Cambridge, 1997.
\bibitem{rudin} Rudin W. {\it Functional analysis.} Second edition. International Series in Pure and Applied Mathematics. McGraw-Hill, Inc., New York, 1991.
\bibitem{SSUZ-pietsch} Semenov E., Sukochev F., Usachev A., Zanin D. {\it Banach limits and traces on $\mathcal{L}_{1,\infty}.$} Adv. Math. {\bf 285} (2015), 568--628.
\bibitem{Shubin-pseudo-2001} Shubin M. {\it Pseudodifferential operators and spectral theory.} Springer-Verlag, Berlin, second edition, 2001.
\bibitem{Simon} Simon B. {\it Trace ideals and their applications.} Second edition. Mathematical Surveys and Monographs, {\bf 120}. American Mathematical Society, Providence, RI, 2005.
\bibitem{subhankulov} Subhankulov M. {\it Tauberian theorems with remainders.} Nauka, Moscow, 1976.
\bibitem{sbik} Sukochev F. {\it On a conjecture of A. Bikchentaev.} Spectral analysis, differential equations and mathematical physics: a festschrift in honor of Fritz Gesztesy's 60th birthday, 327--339, Proc. Sympos. Pure Math., {\bf 87}, Amer. Math. Soc., Providence, RI, 2013.
\bibitem{SUZ-indiana} Sukochev F., Usachev A., Zanin D. {\it Singular traces and residues of the $\zeta$-function.} Indiana U. Math. J., {\bf 66} (2017), no. 4, 1107--1144.
\end{thebibliography}


