\documentclass{article}

\usepackage{amsmath,amsfonts,cite,color}
\usepackage[a4paper,margin=2cm]{geometry}
\usepackage{mathptmx}

\newtheorem{thm}{Theorem}

\renewcommand{\baselinestretch}{0.95}
\newcommand{\archeading}[1]{\vspace{.3cm} \noindent{\bfseries #1} \vspace{.1cm}   }
\renewcommand{\refname}{{\normalsize References}}

\newcommand{\hl}{\color{blue}}
\newcommand{\edcomment}{\color{red}}


\begin{document}

\parindent=20pt
\pagestyle{empty}
\newpage

\archeading{Ten career-best research outputs}

[1] Caspers M., Potapov D., Sukochev F., Zanin D. {\it Weak type commutator and Lipschitz estimates: resolution of the Nazarov-Peller conjecture.} Amer. J. Math., to appear.

[2] Sukochev, F.; Zanin, D. {\it Connes integration formula for the noncommutative plane.} Comm. Math. Phys. {\bf 359} (2018), no. 2, 449--466.

[3] Connes A., Sukochev F., Zanin D. {\it Trace Theorem for quasi-Fuchsian groups.} Mat. Sb. {\bf 208} (2017), no. 10, 59--90.

[4] Junge M., Sukochev F., Zanin D. {\it Embeddings of symmetric operator spaces into $\mathcal{L}_p-$spaces on finite von Neumann algebras.}  Adv. Math. {\bf 312} (2017), 473--546. 

[5]  Lord S., McDonald E., Sukochev F., Zanin D. {\it Quantum differentiability of essentially bounded functions on Euclidean space.} J. Funct. Anal. {\bf 273} (2017), no. 7, 2353--2387.

[6] Jiao Y., Sukochev F., Zanin D. {\it Johnson-Schechtman and Khinchine inequalities in noncommutative probability theory.}  J. Lond. Math. Soc. (2) {\bf 94} (2016), no. 1, 113--140.

[7] Carey A., Rennie A., Sukochev F., Zanin D. {\it Universal measurability and the Hochschild class of the Chern character.} J. Spectr. Theory {\bf 6} (2016), 1--41.


[8] Dykema K., Sukochev F., Zanin D. {\it A decomposition theorem in II$_1-$factors.} J. Reine Angew. Math. {\bf 708} (2015), 97--114.

[9] Sukochev F., Zanin D. {\it Which traces are spectral?} Adv. Math. {\bf 252} (2014), 406--428.


[10] Sukochev F., Zanin D. {\it Traces on symmetrically normed operator ideals.} J. Reine Angew. Math. {\bf 678} (2013), 163--200.

\archeading{Authored books}

[11] Lord S., Sukochev F., Zanin D. {\it Singular traces: Theory and Applications.} De Gruyter Studies in Mathematics. Walter de Gruyter, Berlin, first edition, 2013.

\archeading{Edited books}

\archeading{Book chapters}

\archeading{Refereed journal articles}


[12] Ber A., Sukochev F., Zanin D. {\it Heisenberg relation for locally measurable operators.} Adv. Math. {\bf 335} (2018), 211--230.

[13] Connes A., McDonald E., Sukochev F., Zanin D. {\it Conformal trace theorem for Julia sets of quadratic polynomials.} Ergodic Theory Dynam. Systems. (published online).

[14] Potapov D., Sukochev F., Tomskova A., Zanin D. {\it Frechet differentiability of the norm of $L_p$-spaces associated with arbitrary von Neumann algebras.} Trans. AMS, to appear.

[15] Dykema K., Noles J., Zanin D. {\it Decomposability and norm convergence properties in finite von Neumann algebras.} Integral Equations Operator Theory {\bf 90} (2018), no. 5, Art. 54, 32 pp.

[16] Jiao Y., Zhou D., Wu L., Zanin D. {\it Noncommutative dyadic martingales and Walsh-Fourier series.} J. Lond. Math. Soc. (2) {\bf 97} (2018), no. 3, 550--574.

[17] Levitina G., Sukochev F., Vella D., Zanin D. {\it Schatten class estimates for the Riesz map of massless Dirac operators.} Integral Equations Operator Theory {\bf 90} (2018), no. 2, Art. 19, 36 pp.

[18] Ber A., Chilin V., Sukochev F., Zanin D. {\it Fuglede-Putnam theorem for locally measurable operators.} Proc. Amer. Math. Soc. {\bf 146} (2018), no. 4, 1681--1692.

[19] Dykema K., Sukochev F., Zanin D. {\it An upper triangular decomposition theorem for some unbounded operators affiliated to II$_1-$factors.} Israel J. Math. {\bf 222} (2017), no. 2, 645--709.

[20] Sukochev F., Usachev A., Zanin D. {\it Singular traces and residues of the $\zeta-$function.} Indiana Univ. Math. J. {\bf 66} (2017), no. 4, 1107--1144.

[21] Dykema K., Sukochev F., Zanin D. {\it Determinants associated to traces on operator bimodules.} J. Oper. Th. {\bf 78}:1 (2017), 119--134.

[22] Sukochev F., Zanin D. {\it Fubini theorem in noncommutative geometry.} J. Funct. Anal. {\bf 272} (2017), no. 3, 1230--1264.

[23] Sukochev F., Tulenov K., Zanin D. {\it Nehari type theorem for non-commutative Hardy spaces.} J. Geom. Anal. {\bf 27} (2017), no. 3, 1789--1802.

[24] Jiao Y., Sukochev F., Zanin D., Zhou D. {\it Noncommutative martingale inequalities in symmetric operator spaces.} J. Funct. Anal. {\bf 272} (2017), no. 3, 976--1016.

[25] Carey A., Gesztesy F., Grosse H., Levitina G., Potapov D., Sukochev F., Zanin D. {\it Trace formulas for a class of non-Fredholm operators: a review.} Reviews in Mathematical Physics, Vol. 28, No. 10 (2016) 1630002.

[26] Dykema K., Noles J., Sukochev F., Zanin D. {\it On reduction theory and Brown measure for closed unbounded operators.} J. Funct. Anal. {\bf 271} (2016), no. 12, 3403--3422.

[27] Dykema K., Sukochev F., Zanin D. {\it Algebras of Log-Integrable Functions and Operators.} Complex Anal. Oper. Theory. {\bf 10} (2016), no. 8, 1775--1787.

[28] Jiao Y., Sukochev F., Xie G., Zanin D. $\Phi$-moment inequalities for independent and freely independent random variables.  J. Funct. Anal. 270 (2016), no. 12, 4558--4596.

[29] Carey A., Gesztesy F., Levitina G., Potapov D., Sukochev F., Zanin D. {\it On index theory for non-Fredholm operators: a $(1+1)-$dimensional example.} Math.Nachr. {\bf 289} (2016), no. 5-6, 575--609.

[30] Aubrunn G., Sukochev F., Zanin D. {\it Catalysis in the trace class and weak trace class ideals.} Proc. Amer. Math. Soc. {\bf 144} (2016), no. 6, 2461--2471.

[31] Dykema K., Sukochev F., Zanin D. {\it Holomorphic functional calculus on upper triangular forms in finite von Neumann algebras.} Illinois J. Math. {\bf 59} (2015), no. 3, 819--824.

[32] Astashkin S., Sukochev F., Zanin D. {\it On uniqueness of distribution of a random variable whose independent copies span a subspace in $L_p.$} Studia Math. {\bf 230} (2015), no. 1, 41--57.

[33] Semenov E., Sukochev F., Usachev A., Zanin D. {\it Banach limits and traces on $\mathcal{L}_{1,\infty}.$} Adv. Math. {\bf 285} (2015), 568--628.

[34] Potapov D., Sukochev F., Usachev A., Zanin D. {\it Singular traces and perturbation formulae of higher order.} J. Funct. Anal. {\bf 269} (2015), no. 5, 1441--1481.

[35] Caspers M., Potapov D., Sukochev F., Zanin D. {\it Weak type estimates for the absolute value mapping.} J. Operator Theory {\bf 73} (2015), no. 2, 361--384.

[36] Sukochev F., Usachev A., Zanin D. {\it Dixmier traces generated by exponentiation invariant generalised limits.} J. Noncommut. Geom. {\bf 8} (2014), no. 2, 321--336.

[37] Potapov D., Sukochev F., Tomskova A., Zanin D. {\it Frechet differentiability of the norm of $L_p-$spaces associated with arbitrary von Neumann algebras.} C. R. Math. Acad. Sci. Paris {\bf 352} (2014), no. 11, 923--927.

[38] Astashkin S., Sukochev F., Zanin D. {\it Disjointification inequalities in symmetric quasi-Banach spaces and their applications.} Pacific J. Math. {\bf 270} (2014), no. 2, 257--285.

[39] Potapov D., Sukochev F., Zanin D. {\it Krein's trace theorem revisited.} J. Spectr. Theory {\bf 4} (2014), no. 2, 415--430.

[40] Sukochev F., Zanin D. {\it Dixmier traces are weak$^*$ dense in the set of all fully symmetric traces.} J. Funct. Anal. {\bf 266} (2014), no. 10, 6158--6173.

[41] Levitina G., Pietsch A., Sukochev F., Zanin D. {\it Completeness of quasi-normed operator ideals generated by $s-$numbers.} Indag. Math. (N.S.) {\bf 25} (2014), no. 1, 49--58.

[42] Sukochev F., Usachev A., Zanin D. {\it Generalized limits with additional invariance properties and their applications to noncommutative geometry.} Adv. Math. {\bf 239} (2013), 164--189.

[43] Sukochev F., Usachev A., Zanin D. {\it On the distinction between the classes of Dixmier and Connes-Dixmier traces.} Proc. Amer. Math. Soc. 141 (2013), no. 6, 2169--2179.

[44] Sukochev F., Zanin D. {\it Johnson-Schechtman inequalities in the free probability theory.} J. Funct. Anal. {\bf 263} (2012), no. 10, 2921--2948.

[45] Sukochev F., Zanin D. {\it $\zeta-$function and heat kernel formulae.} J. Funct. Anal. {\bf 260} (2011), no. 8, 2451--2482.

[46] Sedaev A., Sukochev F., Zanin D. {\it Lidskii-type formulae for Dixmier traces.} Integral Equations Operator Theory {\bf 68} (2010), no. 4, 551--572.

[47] Kalton N., Sukochev F., Zanin D. {\it Orbits in symmetric spaces. II.} Studia Math. {\bf 197} (2010), no. 3, 257--274.

[48] Astashkin S., Zanin D., Semenov E., Sukochev F. {\it The Kruglov operator and operators defined by random permutations.} (Russian) Funktsional. Anal. i Prilozhen. {\bf 43} (2009), no. 2, 3--18; translation in Funct. Anal. Appl. {\bf 43} (2009), no. 2, 83--95.

[49] Sukochev F., Zanin D. {\it Orbits in symmetric spaces.} J. Funct. Anal. {\bf 257} (2009), no. 1, 194--218.

[50] Sukochev F., Zanin D. {\it Khinchin inequality and Banach-Saks type properties in rearrangement-invariant spaces.} Studia Math. {\bf 191} (2009), no. 2, 101--122.

[51] Ganikhodzhaev N., Zanin D. {\it On a necessary condition for the ergodicity of quadratic operators defined on a two-dimensional simplex.} (Russian) Uspekhi Mat. Nauk {\bf 59} (2004), no. 3 (357), 161--162; translation in Russian Math. Surveys {\bf 59} (2004), no. 3, 571--572.

\archeading{Fully refereed conference proceedings}

\archeading{Additional research outputs (including non-traditional research outputs)}
\end{document}